Verifying Demonstrations

### 2019-09-12 paper/DB-anon-cred.tex
Changes UWBPR key from \sk to k in DBS protocol
Adds HW TF argument for the additional PK

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\DBSprove[\sk, g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[\sk, g, q, A]\):
    \\
    \midrule

@@

    Load \(\sk\) into \(\UWBPR\)
    &
    & Load \(\sk\) into \(\UWBPR\)
    \\

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
    \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{DBSHW-overview}
\end{figure*}

@@

>>>>

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[k, g, q, A]\):
    \\
    \midrule

@@

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
    \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol actually proves \(\PK[\alpha, \sk_P][\hat A = g^\alpha 
      \hat g^{\sk_P}]\).
    This is for the device to prove knowledge of the key~\(\sk_P\) to prevent 
    \ac{DBTF}.
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{DBSHW-overview}
\end{figure*}

@@

The hardware device (\DBSHW) could commit \ac{DBTF}\footnote{%
  Arguably, this should not be an issue since the device is trusted.
  However, we include this construction because it is a neat way to provide 
  \ac{DBTF} resistance for this part of the protocol as well.
  To not have this feature, one simply adds the authenticated key exchange step 
  to \cref{SchnorrFigure}.
} by giving the key~\(k\) to a malicious prover --- this would allow that 
prover to authenticate once.
To prevent this possibility we include a proof of knowledge of the device's 
private key~\(\sk_P\), \ie that \(\pk_P = \hat g^{\sk_P}\).
This way, an accomplice can only pass if he is given both \(k\) and \(\sk_P\).
